\prefacesection{Acknowledgments}

As the last page I write of this document, I would like to end by thanking all those who contributed from my beginnings as a student to the culmination of my degree career through this project.

Especially:

To Lili, Mijal and Mariano, tutors of this project. They got me interested in the project from the first meeting. Always motivated and ready to help me in whatever it took to move forward. They gave me the freedom to carry out the work, the tools, their knowledge and their support to obtain the best possible results.

To the group of excellent professionals that comprise the Bicentennial Micro and Nanoelectronics Center. They received me from the first day as one of them and were always attentive to help me with what I needed.

To Gustavo Giménez for his enormous help with the characterization, his master class in electrochemistry and his recommendations for the project.

To the Instituto Nacional de Tecnología Industrial for providing me with the materials, space and help of its members to carry out the work.

To the Universidad Nacional de San Martín, for providing excellent free public education.

To Eng. Sinderman, Director of the Career, for having his office always open, ready to listen and help the students so that they can achieve their goals. Also, for giving the best Circuit Theory classes that an electronics student can ask for.

To Eng. Polenta for giving the best and most interesting classes (also the most difficult) of the career.

To the friends that I have been making throughout these years, especially to Gastón, Alan and Mauri with whom we promote each other in the last great efforts of finals and projects.

To my Lifelong friends Lucas, Agustin, Andi, Fede, Dexter and Stefan.

To my uncles and cousins for supporting me and helping me when I needed it most.

To my grandparents, who are no longer here but always inspired me to fight and strive to achieve what you want.

To my mother and father who supported me in all my decisions and gave me everything or more than I needed.

Last but not least, dedicate it especially to Lucila, who always supported me, gives me her joy and her love day by day.